---
title: "SPR2 - Markdown for Data Exploration"
author: "Uk"
date: "2024-03-13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Headings

# Heading 1 (big heading)
## Heading 2 (medium sized heading)
### Heading 3 (small sized heading)
#### THE MORE THE NUMBER OF (#) THE SMALLER THE HEADING

# BOLD AND ITALICS
### Using two * at the beginning and end of a word or sentence will **bold** it
### Using one * at the beginning and end of a word or sentence will *italicize* it
*I want to italicise this sentence*
I want to italicise this *word*
**I want to bold this sentence**
I want to bold this **word**

# Bullet point
Use dashes (-) to make bullet points and you must always add a space after the dashes(-)

- bullet 1
- bullet 2
- bullet 3

# Insert quotes
> "No question is a silly question - Sonia Bejarano"

# Insert a link
you can insert aa link using [here] as follows:

you can learn all about R markdown in this [link](https://rmarkdown.rstudio.com)

# Inserting code chunks in Rmarkdown
learning how to insert code is one important thing before we move to data exploration.
This is the real power of markdown.

- This is one of the ways to insert code chunks (typing the below manually)
- use ctrl+shift+l to insert a blank space

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
# Load my packages
library(tidyverse)
```


